%Syllabus
%Copyright (C) 2019  Patrick Diehl
%
%This program is free software: you can redistribute it and/or modify
%it under the terms of the GNU General Public License as published by
%the Free Software Foundation, either version 3 of the License, or
%(at your option) any later version.

%This program is distributed in the hope that it will be useful,
%but WITHOUT ANY WARRANTY; without even the implied warranty of
%MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%GNU General Public License for more details.

%You should have received a copy of the GNU General Public License
%along with this program.  If not, see <http://www.gnu.org/licenses/>.
\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lastpage}

\usepackage{pgfplotstable}
\usepackage{booktabs}

\input{../template/variables.tex}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{\coursesemester}
\lhead{Syllabus, \coursename~\coursetitle}
\rfoot{Page \thepage~of \pageref{LastPage}}
\lfoot{Last updated: \today}

\usepackage{ifxetex}

\ifxetex
\usepackage{fontspec}
\setmainfont{Raleway}
\fi

\usepackage[
    type={CC},
    modifier={by-nc-nd},
    version={4.0},
]{doclicense}

\usepackage{xfrac}


\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Course summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The course objectives are the following:
\begin{itemize}
\item To teach basic research methods of relevance to thesis and dissertation research projects
conducted by graduate students.
\item To teach graduate students how to prepare a written research proposal suitable for an MS or
PhD research project and general examination.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Course Instructors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular}{lll}
Patrick Diehl & Course Director & \url{patrickdiehl@lsu.edu} \\ 
Noujoude Nader & Instructor & \url{nnader@lsu.edu} \\ 
Krystal Kirby & Instructor & \url{kkirby@marybird.com} \\
Christopher Schneiders & Instructor &  \url{cschneider@marybird.com}
\end{tabular} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Prerequisites}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
None.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Lectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\coursedate, \courselocation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Important dates}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item Midterm exam:  TBA, \courselocation
\item Final exams: TBA, \courselocation
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Reading}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We will use material from the following books in the course:

\begin{itemize}
\item Andrew, Koenig. Accelerated C++: practical programming by example. Pearson Education India, 2000.
\item Stroustrup, Bjarne. Programming: principles and practice using C++. Pearson Education, 2014.
\item Chacon Scott and Ben Straub. Pro git. Apress, 2014. \href{https://github.com/progit/progit2/releases/download/2.1.146/progit.pdf}{Ebook}
\item Scott, Craig. Professional CMake: A Practical Guide, 2018.
\item Andreas, M\"uller and Sarah Guido  Introduction to Machine Learning with Python: A Guide for Data Scientists. O'Reilly, Media. 2016
\item Field Cady. The Data Science Handbook. Wiley. 2017
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Other resources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Web page: \url{\courseurl}
\end{itemize}

Please don’t hesitate to ask questions related to the course by sending me emails: \href{mailto:patrickdiehl@lsu.edu}{Patrick Diehl}. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Projects, Homework, and Quizzes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Grading}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Each instructor will assign you homework, including online learning modules. Unless otherwise indicated, all assignments are due one week after they are assigned. We will use GitHub\textsuperscript{\textregistered}~Classroom for to submit the exercises.  Overall, in the end of the semester $\geq$ 97\% of all points or more will give you an ‘A+’,  $\geq$ 93\% `A`,  $\geq$ 90\% `A-`,  $\geq$  87\% `B+`,  $\geq$  83\% `B`,  $\geq$  80\% `B-`,  $\geq$ 77\% `C+`,  $\geq$ 73\% `C`.  $\geq$  70\% `C-`,  $\geq$  67\% `D+`.  $\geq$  63\% `D`,  $\geq$  60\% `D-`, and $<$ 60 `F`. However, I’m sure that will not happen to anyone.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Topics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Table~\ref{tab:detailed:outiine} shows the topics of this course and the instructors.

\begin{table}[tbp]
\pgfplotstabletypeset[
col sep = comma,
every head row/.style={before row=\toprule,after row=\midrule},
every last row/.style={after row=\bottomrule},
display columns/0/.style={string type},
display columns/1/.style={string type},
display columns/2/.style={string type}
]{../timetable/content.csv}
\caption{Detailed course outline. There  is  also some flexibility in shortening some of these topics and adding other advanced topics.}
\label{tab:detailed:outiine}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Office hours}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Every Wednesday from 11:00 to 12:00 at the Center of Computation \& Technology 
for the course director Dr.\ Diehl. Please contact the course instructors for
scheduling office hours.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Course Policy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Grading}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
It is course policy that whoever graded something will be responsible for handling grading disputes. I will grade the midterm exam and the final exam. The grader will grade the homework and the project. Grades become final one week after homework or exam is handed back. This should leave ample time to resolve grading disputes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Homework Standards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
All homework and the project will be submitted using GitHub\textsuperscript{\textregistered}~Classroom. There will be instructions on the first exercise sheet. All work submitted must carry the student's name and must have sufficient comments and be well organized. A work that can not be open or read easily will get less credits.  A  reasonable standard  of  English  expression  and  grammar  is  also  required.  The  same  requirements  apply  to  exams. Additional requirements   may   apply   for   any   of   the   separate   assignments   and   will   be   outlined   in   the   corresponding descriptions.
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Cheating}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cheating is a very serious offense and will not be tolerated. Supplying others with homework solutions or materials is forbidden. The  policy  is  that  the supplier and the receiver of information will both be dealt with in accordance with and as outlined by the LSU Code of Student Conduct\footnote{\url{https://www.lsu.edu/saa/students/codeofconduct.php}}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Programming standards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For this course obviously your submitted code should compile and run. Due to the complexity of the program, no credit can be given for a program that does not compile. If a program only partly runs, only partial credit will be given.



\doclicenseThis

\end{document}
